Scientific computing applications are being increasingly deployed on cloud computing platforms.
%
Transient servers can be used to lower the costs of running applications on the cloud.
%
However, the frequent preemptions and resource heterogeneity of these transient servers introduces many challenges in their effective and efficient use.
%
In this paper, we develop techniques for modeling and mitigating preemptions of transient cloud servers, and present \sysname, a software framework for running scientific computing applications at low cost on the cloud.
%
\sysname's design is guided by our observation that most scientific computing applications (such as simulations) are deployed as ``bag'' of jobs, which represent multiple instantiations of the same computation with different physical and computational parameters.
%
Treating bags of jobs as a unit of execution enables simple and powerful policies for optimizing the cost, makespan, and ease of deployment. 
%
\sysname uses Google Cloud Preemptible VMs, and provides the first empirical and analytical model for their preemptions.
%
\sysname reduces costs by $5\times$ compared to conventional cloud deployments, and makespans by up to $10\times$ compared to conventional HPC clusters.




% We show that optimizing across an entire bag of jobs and being cognizant of the relation between different jobs in a bag, can enable simple and powerful policies for optimizing cost, makespan, and ease of deployment. 


% present SciSpot, a software framework for running scientific applications on transient cloud servers.


% Transient cloud servers can yield significantly lower costs compared to traditional on-demand cloud servers. 
% However, due to their preemptible nature and heterogeneity, their effective use remains challenging.
% %
% % 
% We perform a large-scale, first-of-its-kind empirical measurement and analytical modeling involving over a thousand Google preemptible VMs. 
% Our policies for tackling the resource heterogeneity and transient availability of cloud VMs build on a key insight: most scientific computing applications are deployed as ``bag'' of jobs, which represent multiple instantiations of the same computation with different parameters.
% SciSpot yields a cost saving of 70\% compared to traditional cloud deployments, and a makespan reduction of 20\% compared to a conventional HPC clusters. 

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "paper"
%%% End:
